openarchaeoCollaboration

### 2021-06-15 analysis/paper.Rmd
Expand analysis of contributors

```{r plot-gh_contributors-histogram}
oarch %>%
  drop_na(gh_repo) %>%
  unnest(gh_contribs) %>%
  group_by(gh_repo) %>%
  summarise(n = n(), .groups = "drop") %>%
  ggplot(aes(x = n)) +
  geom_histogram() +
  scale_x_log10() +
  labs(
    title = "Repository contributors",
    caption = "Data: <https://open-archaeo.info> and the GitHub API",
    x = "Number of contributors", y = "Number of repositories"
  )

ZB: Add a chart, limited to repos with more than 1 contributor. It should present how evenly distributed commits are across all contributors. So maybe a percent stacked bar chart, with bars representing a repository, with each bar broken down into sections representing each inidividual contributor, and each section's size representing the percentage of the individual's commits out of the total from the repo.

>>>>

```{r plot-gh_contributors-histogram}
oarch %>%
  drop_na(gh_repo) %>%
  unnest(gh_contribs) %>%
  group_by(gh_repo) %>%
  summarise(n = n(), .groups = "drop") %>%
  ggplot(aes(x = n)) +
  geom_histogram() +
  scale_x_log10() +
  labs(
    title = "Repository contributors",
    x = "Number of contributors", y = "Repositories",
    caption = "Data: open-archaeo.info and GitHub API"
  ) +
  theme_oarch()

# Export for slides (half slide)
# ggsave("figures/contrib-hist.png", width = 127, height = 127, units = "mm")
```

```{r plot-contrib-dist}
oarch %>% 
  unnest(gh_contribs) %>% 
  drop_na(contributor) %>% 
  group_by(item_name) %>% 
  mutate(n_contributors = n()) %>% 
  filter(n_contributors > 1) %>% 
  mutate(big_boy = ifelse(contributions == max(contributions), 
                          "Main contributor", "Other contributors")) %>% 
  ggplot(aes(x = item_name, y = contributions, 
             group = contributor,
             fill = big_boy)) +
  geom_col(position = "fill", colour = "white") +
  scale_y_continuous(labels = scales::percent) +
  labs(x = "Repository", y = "Contributions",
       fill = NULL) +
  coord_flip() +
  theme_oarch() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

# Export for slides (half slide)
# ggsave("figures/contrib-dist.png", width = 127, height = 127, units = "mm")
```
